Practice with parametric distributions

### 2017-07-12 practice_parametricdist.Rmd
tried to construct probability plots

### finding parameter estimates with flexsurv package
```{r}
library(flexsurv)

#weibull distribution
weibull <- flexsurvreg(surv_object~1, data = out1, dist = "weibull")
weibull
plot(weibull)
#shape = 0.228, scale = 1320000, AIC = 123791.7
qqplot(rweibull(1e+5, shape = 0.228, scale = 1320000), out1$time_until_answer)

#exponential distribution
exp <- flexsurvreg(surv_object~1, data = out1, dist = "exp")
exp
plot(exp)
#rate = 4.98e-07, AIC = 153610

#lognormal distribution
lnormal <- flexsurvreg(surv_object~1, data = out1, dist = "lnorm")
lnormal
plot(lnormal)
#meanlog = 12.05, sdlog = 4.86, AIC = 122112.1

#logistic distribution
logistic <- flexsurvreg(surv_object~1, data = out1, dist = "llogis")
logistic
plot(logistic)
#shape = 0.332, scale = 119000, AIC = 122482
```

### setting up probability plots to assess fit
```{r}
# library(car) #for the qqPlot function
# par(mfrow = c(2,2))
# qqPlot(out1$time_until_answer, distribution = "weibull", param.list = list(shape = 0.228, scale = 1320000), plot.type = "Q-Q")
qqplot(rweibull(n = 8000, shape = 0.228, scale = 1320000), out1$time_until_answer)
abline(0,1)
qqplot(rlnorm(n = 8000, meanlog = 12.05, sdlog = 4.86), out1$time_until_answer)
abline(0,1)
#are the plots actually following the line?- maybe scale too large to see it correctly 
```

### learning about flexsurvreg 
```{r}
time <- c(5,8,12,24,32,17,16,17,19,30)
censor <- c(1,1,1,1,1,1,0,0,0,0)
example <- data.frame(time, censor)

@@

### parametric distributions using fitdistrplus package NOT WORKINGG
```{r}
library(fitdistrplus)

@@

### practicing with fitdistcens function 
```{r}
data("salinity")
str(salinity)
data("smokedfish")

>>>>

### finding parameter estimates with flexsurv package
```{r}
surv_object <- Surv(out1$time_until_answer, out1$answered, type = "right")

library(flexsurv)

weibull <- flexsurvreg(surv_object~1, data = out1, dist = "weibull")
weibull
plot(weibull)

exp <- flexsurvreg(surv_object~1, data = out1, dist = "exp")
exp
plot(exp)

lnormal <- flexsurvreg(surv_object~1, data = out1, dist = "lnorm")
lnormal
plot(lnormal)
#has lowest AIC of the 4 distributions

logistic <- flexsurvreg(surv_object~1, data = out1, dist = "llogis")
logistic
plot(logistic)

### setting up probability plots to assess fit
```{r}
#are the plots actually following the line?- maybe scale too large to see it correctly 
qqplot(rweibull(15000, shape = 2.26e-01, scale = 1.32e+06), out1$time_until_answer, xlab = "rweibull values", ylab = "seconds")
abline(0,1)

#narrowed scope of x-axis to get a closer look at the plot-data does not fit a weibull distribution (not sure if did this correctly)
qqplot(rweibull(15000, shape = 2.26e-01, scale = 1.32e+06), out1$time_until_answer, xlim = c(0,1e+8), xlab = "rweibull values", ylab = "seconds")
abline(0,1)
#data doesn't fit weibull distribution

qqplot(rexp(15000, rate = 4.86e-07), out1$time_until_answer, xlab = "rexp values", ylab = "seconds")
abline(0,1)
#data doesn't fit an exponential distribution either

qqplot(rlnorm(15000, meanlog = 12.1129, sdlog = 4.8951), out1$time_until_answer, xlab = "rlnorm values", ylab = "seconds", xlim = c(0, 5e+7))
abline(0,1)
#data doesn't fit lognormal distribution

qqplot(rlogis(15000, location = 3.30e-01, scale = 1.28e+05), out1$time_until_answer)
abline(0,1)
#data does not fit logistic distribution 
```

### learning about flexsurvreg (using different data)
```{r}
time <- c(5,8,12,24,32,17,16,17,19,30)
censor <- c(1,1,1,1,1,1,0,0,0,0)
example <- data.frame(time, censor)

@@

### trying to apply fitdistrplus functions to data (NOT WORKING)
```{r}
library(fitdistrplus)

@@

### practicing with fitdistcens function on different dataset 
```{r}
data("salinity")
str(salinity)
data("smokedfish")
